Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-11-24 PAPER/paper_mc.tex
Matt's edits to the figure legends.

%% Figure 2
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure2.pdf} 
%}
\caption{\textbf{Number of putative SNVs in WGS versus WGA, as called by SomaticSniper before filtering.} For each patient (represented by one point), we compared the number of SNVs called in the WGS sample ($y$-axis) versus the number of SNVs called in the WGA sample ($x$-axis). As expected, the number of mutations found in one replicate correlates with the number of mutations found in the other replicate (Spearman $\rho=0.42$, $S=16142$, $P=0.002$). The line shown is $y=x$, so points falling below the line agree with the hypothesis that an additional amplification step produces more sequencing errors in a sample. }
\label{fig:C282_v_C484}
\end{figure}

%% Figure 3
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure3.pdf} 
%}
\caption{\textbf{Number of putative SNVs per sample does not correlate with the number of putative SNVs recoverable in both replicates.} To test the hypothesis that samples with a greater number of SNVs also have a greater number of errors, and consequently a smaller percentage of SNVs recovered in the overlap between replicates, we compared the percentage of putative SNVs recovered in the overlap between replicates for a sample ($y$-axis) versus the number of mutations in that sample ($x$-axis). We found no correlation (Spearman $\rho=0.05$, $S=29268$, $P=0.68$), suggesting that higher numbers of SNVs in a sample may not be only due to errors. We calculated the percent overlap in two ways: with reference to the total number of putative SNVs in the WGS sample (red) and with reference to the total number of putative SNVs in the WGA sample (black). The correlation was calculated with respect to WGA.}
\label{fig:unfiltered_total_muts}
\end{figure}

%% Figure 4
\begin{figure}
%\centerline{
%\includegraphics[width=6in]{Figure4.pdf} 
%}
\caption{\textbf{Independent performance of the individual filters of the overlap between replicates.} For each filter (names given on the $x$-axis, with detailed description in Table 1), we looked at the number of mutations removed by a given filter in a given sample on a log scale \textit{(above)}, and the percentage of the WGS--WGA overlap removed by the filter \textit{(below)}, per sample. The LOH and VAQ filters removed a large number of putative SNVs and portion of the overlap. The <10\% filter removed very few putative SNVs and almost none of the overlap. The 10bp-SNV, 10bp-INDEL, and dbSNP filters removed an intermediate number of putative SNVs (~100), but only a very small portion of the overlap, making them the best performers on the overlap data. }
\label{fig:boxplot_filtered}
\end{figure}

%%Figure 5
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure5.pdf} 
%}
\caption{\textbf{Independent performance of individual filters of the difference between replicates.} For each sample, we compared the size of the difference between replicates (the number of SNVs found in only one of WGS or WGA) to the size of the overlap between replicates (the number of SNVs recovered from both the WGA and WGS replicates). \textit{(top left)} A scatter plot of the ratio, per sample per filter, of putative SNVs removed from the difference versus the overlap of WGS and WGA ($WGS \triangle WGA / WGS \cap WGA$). \textit{(top right)} Boxplot of the same data, divided by filter on the $x$-axis. \textit{(below)} Plot of the percentage difference in the Jaccard(WGS, WGA), with Jaccard=$|WGS \cap WGA|/|WGS \cup WGA|$, before and after the action of each filter (each filter was run on the whole data set independently).}
\label{fig:diffset}
\end{figure}

%%Figure 6
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure6.pdf} 
%}
\caption{ \textbf{Replicate SNVs filtered out by LOH and VAQ are almost completely non-overlapping and cover most of the sample.} Across samples, as the length of the overlap between WGS and WGA increases ($x$-axis),  \textit{(above)} the percentage of the overlap filtered out by LOH increases, and \textit{(below)} the percentage of the overlap filtered out by VAQ decreases. The two are almost (but not quite) perfect inverses: putative SNPs filtered by LOH and VAQ cover almost the entire overlap, and together sum to nearly 100\% of the overlap.}
\label{fig:LOH-VAQ_all}
\end{figure}

>>>>

%% Figure 2
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure2.pdf} 
%}
\caption{\textbf{Number of putative SNVs in WGS versus WGA before filtering.} For each patient (represented by one point), we compared the number of SNVs called in the WGS sample ($y$-axis) versus the number of SNVs called in the WGA sample ($x$-axis). As expected, the number of mutations found in one replicate correlates with the number of mutations found in the other replicate (Spearman $\rho=0.42$, $S=16142$, $P=0.002$). The line shown is $y=x$ (WGS = WGA); points falling below the line support the hypothesis that WGA introduces additional spurious variants in a sample. }
\label{fig:C282_v_C484}
\end{figure}

%% Figure 3
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure3.pdf} 
%}
\caption{\textbf{Total number of SNVs per sample does not correlate with the number of putative SNVs recovered after filtering.} To test the hypothesis that samples with a greater number of SNVs also have a greater number of errors that impede recovery of putative SNVs, we compared the percentage of putative SNVs recovered in the overlap between replicates for a sample ($y$-axis) to the number of total number of mutations in that sample ($x$-axis).  We found no correlation (Spearman $\rho=0.05$, $S=29268$, $P=0.68$), suggesting that higher total SNV counts in a sample may due to additional factors other than errors. We calculated the percent overlap in two ways: with reference to the total number of putative SNVs in the WGS sample (red) and with reference to the total number of putative SNVs in the WGA sample (black). The correlation was calculated with respect to WGA.}
\label{fig:unfiltered_total_muts}
\end{figure}

%% Figure 4
\begin{figure}
%\centerline{
%\includegraphics[width=6in]{Figure4.pdf} 
%}
\caption{\textbf{Effect of individual filters on the overlap between replicates.} For each filter (names given on the $x$-axis, with detailed description in Table 1), we looked at the number of mutations removed by a given filter in a given sample \textit{(above)}, and the percentage of the WGS--WGA overlap removed by the filter \textit{(below)}, per sample. The LOH and VAQ filters removed a large number of putative SNVs and portion of the overlap. The <10\% filter removed very few putative SNVs and almost none of the overlap. The 10bp-SNV, 10bp-INDEL, and dbSNP filters removed an intermediate number of putative SNVs (~100), but only a very small portion of the overlap, making them the best performers on the overlap data.  SNV counts are plotted on a log scale. }
\label{fig:boxplot_filtered}
\end{figure}

%%Figure 5
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure5.pdf} 
%}
\caption{\textbf{Effect of individual filters on the difference between replicates.} For each sample, we compared the size of the difference between replicates (the number of SNVs found in only one of WGS or WGA) to the size of the overlap between replicates (the number of SNVs recovered from both the WGA and WGS replicates). \textit{(top left)} A scatter plot of the ratio, per sample per filter, of putative SNVs removed from the difference versus the overlap of WGS and WGA ($WGS \triangle WGA / WGS \cap WGA$). \textit{(top right)} Boxplot of the same data, divided by filter on the $x$-axis. \textit{(below)} Plot of the percentage difference in the Jaccard(WGS, WGA), with Jaccard=$|WGS \cap WGA|/|WGS \cup WGA|$, before and after the action of each filter (each filter was run on the whole data set independently).}
\label{fig:diffset}
\end{figure}

%%Figure 6
\begin{figure}
%\centerline{
%\includegraphics[width=5in]{Figure6.pdf} 
%}
\caption{ \textbf{LOH and VAQ filters remove almost completely different sets of mutations and cover most of the sample.} Across samples, as the length of the overlap between WGS and WGA increases ($x$-axis),  \textit{(above)} the percentage of the overlap filtered out by LOH increases, and \textit{(below)} the percentage of the overlap filtered out by VAQ decreases. The two are almost (but not quite) perfect inverses: putative SNPs filtered by LOH and VAQ cover almost the entire overlap, and together sum to nearly 100\% of the overlap.}
\label{fig:LOH-VAQ_all}
\end{figure}
